The error in Bayesian phylogenetic reconstruction when speciation co-occurs

### 2020-03-31 razzo-results.tex
Discuss all figures in the results

@@

All intermediate data can be downloaded from \url{https://richelbilderbeek.nl/razzo_project_20200204.zip}.

>>>>

98% of all runs finished within 10 days. 
Of these runs, figure \ref{fig:esses} shows the distribution 
of their effective samples sizes, with 88\% above the recommended 
value of 200.

Figure \ref{fig:n_taxa} shows the number of taxa for all runs. 
Most runs have less than 100 taxa, of which the median and mean both lie
beloe 30 taxa.

@@

All simulated data can be downloaded from \url{https://richelbilderbeek.nl/razzo_project_20200204.zip}.
